Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
edits to 2.4

Recall from Sec.~\ref{mathematicalFraming} that we want the DSL maximizing $\int \lowerBound\;\mathrm{d}\theta$.
We replace this marginal with an AIC approximation, giving the following objective for DSL induction:
\begin{align}
\nonumber  \log \probability[\mathcal{D}] + \argmax_{\theta}& \sum_{x\in X}\log \sum_{p\in \mathcal{F}_x}\probability[x|p]\probability[p|\mathcal{D},\theta]\\
&+  \log P(\theta|\mathcal{D}) - ||\theta||_0 \label{AIC}
  \end{align}

@@

We define a prior distribution over DSLs which penalizes the sizes of the $\lambda$-calculus expressions in the DSL, and put a Dirichlet prior over the weight vector:
\begin{align*}
  \probability[\mathcal{D}]&\propto\exp\left(-\lambda\sum_{p\in \mathcal{D}}\text{size}(p) \right)\\
  P(\theta|\mathcal{D})& = \text{Dir}(\theta|\alpha)
\end{align*}
where $\text{size}(p)$  measures the size of the syntax tree of program $p$,
$\lambda$ is a hyperparameter that acts as a regularizer on the size of the DSL,
and $\alpha$ is a concentration parameter controlling the smoothness of the prior over $\theta$.
%Alg.~\ref{grammarInductionAlgorithm} specifies the DSL induction algorithm.

To appropriately score each proposed $\mathcal{D}$ we must reestimate the weight vector $\theta$.
Although this problem may seem 
very similar to estimating the parameters of a probabilistic context free grammar,
for which we have effective approaches like the Inside/Outside algorithm~\cite{international2000derivation},
a DSL in \system may be context-sensitive due to the presence of variables
in the programs and also due to the polymorphic typing system.
In the Supplement we derive a tractable MAP estimator for $\theta$.

>>>>

Recall from Sec.~\ref{mathematicalFraming} that we want the DSL maximizing $\int \lowerBound\;\mathrm{d}\theta$.
We replace this marginal with an AIC approximation, giving the following objective for DSL induction:
\begin{align}
  \nonumber
    \log \probability[\mathcal{D}] + \argmax_{\theta}&\sum_{x\in X}\log \sum_{p\in \mathcal{F}_x}\probability[x|p]\probability[p|\mathcal{D},\theta]\\
  &+ \log \probability[\theta|\mathcal{D}] - \|\theta\|_0 \label{AIC}
  \end{align}

@@

We define a prior distribution over DSLs which penalizes the sizes of the $\lambda$-calculus expressions in the DSL, and put a Dirichlet prior over the weight vector:
\begin{align*}
  \probability[\mathcal{D}]&\propto\exp\left(-\lambda\sum_{p\in \mathcal{D}}\text{size}(p) \right)\\
  \probability[\theta|\mathcal{D}]& = \text{Dir}(\theta|\alpha)
\end{align*}
where $\text{size}(p)$  measures the size of the syntax tree of program $p$,
$\lambda$ is a hyperparameter that acts as a regularizer on the size of the DSL,
and $\alpha$ is a concentration parameter controlling the smoothness of the prior over $\theta$.
%Alg.~\ref{grammarInductionAlgorithm} specifies the DSL induction algorithm.

To appropriately score each proposed $\mathcal{D}$ we must reestimate the weight vector $\theta$.
Although this problem may seem 
very similar to estimating the parameters of a probabilistic context free grammar (PCFG),
for which we have effective approaches like the Inside/Outside algorithm~\cite{international2000derivation},
a DSL in \system may be context-sensitive due to the presence of variables
in the programs and also due to the polymorphic typing system.
In the Supplement we derive a tractable MAP estimator for $\theta$.
